---
title: "Age Compared by Class Sections"
author: "Bridget East"
date: "10/10/18"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  
We start by loading the data into 2 data frames

```{r include=FALSE,echo=FALSE}
library(readr)
Sec02 <- read_csv("Class_Survey_Sec02.csv")
Sec23 <- read_csv("Class_Survey_Sec23.csv")
Sec02 <- mutate(Sec02,sect="PM")
Sec23 <- mutate(Sec23,sect="Eve")
alldat <- bind_rows(Sec02,Sec23)
```



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
  
After combining the survey data from both the evening and night statistics classes, we took the merged survey data and added a new variabke saying which class section (sect) the data is from, we then take the data and compare the evening (eve) and night (pm) classes. we use that to answer our questions. there are approximately 40 responses in each data set and 83 over all.
  
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
  
```{r include=FALSE,echo=FALSE}
survey <- read.table("D:/Project_folders/Class_Survey/alldata.csv", header=TRUE, sep=",", na.strings="NA", 
  dec=".", strip.white=TRUE)
```
  
```{r}
Boxplot(Age_yrs~sect, data=survey, id=list(method="y"))
```
  
The box plot shows that the evening class data is higher than the night class data. the two sets of data look disjoint with the evening class being higher than the night class. This indicates a differences and the evening class is perhaps older.
  
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
numSummary(survey[,"Age_yrs", drop=FALSE], groups=survey$sect, statistics=c("mean", "sd", "IQR", "quantiles"), 
  quantiles=c(0,.25,.5,.75,1))
```
  
There is enough data to support us in rejecting the null hypothesis.
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
t.test(Age_yrs~sect, alternative='two.sided', conf.level=.95, var.equal=FALSE, data=survey)
```
  
  
```{r}
source("bootstrap.R")
a=na.omit(survey$Age_yrs[survey$sect=="PM"])
b=na.omit(survey$Age_yrs[survey$sect=="Eve"])
bootstrp(a,b,1000)
```

  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->












