---
title: "Breath Hold Times Between Males and Females"
author: "Bridget East"
date: "10/10/18"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  
We start by loading the data into 2 data frames

```{r include=FALSE, echo=FALSE}
library(readr)
Sec02 <- read_csv("Class_Survey_Sec02.csv")
Sec23 <- read_csv("Class_Survey_Sec23.csv")
Sec02 <- mutate(Sec02,sect="PM")
Sec23 <- mutate(Sec23,sect="Eve")
alldat <- bind_rows(Sec02,Sec23)
```



# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
We are comparing the data between time up and down the stairs, and gender. we look at graphical and numerical forms of the data, and perfom t-tests and bootstrap.
  
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
  

```{r}
alldata <- read.table("D:/Project_folders/Class_Survey/alldata.csv", header=TRUE, sep=",", na.strings="NA", 
  dec=".", strip.white=TRUE)
```

```{r}
Boxplot(Breathold~Gender, data=alldata, id=list(method="y"))
```
  
The box plot shows that the means are very close, but the upper percentile of males is higher then the upper percentile of females.
  
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
numSummary(alldata[,"Breathold", drop=FALSE], groups=alldata$Gender, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```
  
There is not a significant difference in the means of males and females breatholds.  
  
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
t.test(Breathold~Gender, alternative='two.sided', conf.level=.95, var.equal=FALSE, data=alldata)
```
  
  
```{r}
source("bootstrap.R")
a=na.omit(alldata$Breathold[alldata$Gender=="M"])
b=na.omit(alldata$Breathold[alldata$Gender=="F"])
bootstrp(a,b,1000)
```

  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->




