---
title: "Stair Times (Males vs. Female)"
author: "Bridget East"
date: "10/10/18"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  

```{r include=FALSE,echo=FALSE}
library(readr)
Sec02 <- read_csv("Class_Survey_Sec02.csv")
Sec23 <- read_csv("Class_Survey_Sec23.csv")
Sec02 <- mutate(Sec02,sect="PM")
Sec23 <- mutate(Sec23,sect="Eve")
alldat <- bind_rows(Sec02,Sec23)
```

We will start off by loading the data from the class survey, this is a survey the class filled out at the beginning of the semester, and we will observe the various categories of data included. The data was taken from two sections, an evening class and a night class, the catagories include sex, breathold time, time up/down the stairs and etc.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
  
We are comparing the data between time up and down the stairs, and gender. We will look at graphical and numerical forms of the data, and perfom t-tests and bootstrap. From this data we can determine if there is a difference in the time up and down of men and women. My hypothesis is that the men will have faster times because they are usually bigger and have more muscle mass.
  
#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
  

```{r include=FALSE,echo=FALSE}
alldata <- read.table("D:/Project_folders/Class_Survey/alldata.csv", header=TRUE, sep=",", na.strings="NA", 
  dec=".", strip.white=TRUE)
```

```{r}
Boxplot(time_down_up~Gender, data=alldata, id=list(method="y"))
```
  
The box plot shows that the female data is higher than the male data. The two sets of data look disjoint with the female being higher than the male. This indicates a difference and the males are perhaps quicker when going up and down stairs.
  
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
numSummary(alldata[,"time_down_up", drop=FALSE], groups=alldata$Gender, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```
  
There is a significant difference in the means of males and females times up and down the stairs. The female mean is 30, while the male mean is 24. I believe this is a large difference.
It seems as though males have faster times going up and down the stairs.
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
t.test(time_down_up~Gender, alternative='two.sided', conf.level=.95, var.equal=FALSE, data=alldata)
```
  
The p value is too low so I choose to reject the null hypothesis. If it were higher it would mean there was a larger difference and more correlation.
  
```{r}
source("bootstrap.R")
a=na.omit(alldata$time_down_up[alldata$Gender=="M"])
b=na.omit(alldata$time_down_up[alldata$Gender=="F"])
bootstrp(a,b,1000)
```
  
The p value is still too low although it looks like males are faster. The pvalue in bootstrap was fairly higher then in the t test.
  
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Males seem to have faster times, but we reject the null hypothesis. We used t tests and bootstrap test and compared them, and it was interesting getting to see data from our class. 






